---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TimeDependentCIndex

<!-- badges: start -->
<!-- badges: end -->

This contains R-code and example data for the statistical method for evaluating a time-dependent C-index for recurent event data, described in:"Wang J, Jiang X, Ning J. Evaluating dynamic and predictive discrimination for recurrent event models: use of a time-dependent C-index. Biostatistics. Submitted." 

## Installation

You can install the development version of TimeDependentCIndex from [GitHub](https://github.com/) with:

```{r}
library(devtools)
devtools::install_github("lilyxj91/TimeDependentCIndex",force = TRUE)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(TimeDependentCIndex)

### Define the parameters
n.var<-3  ## number of predictors
B<-200  ## number of perturbations
train.data = TrainData
validate.data = ValidateData
```

```{r}
### Calculate alpha values and perturbation alpha values
### May take hours to run depending on the pre-specified number of perturbations

results<-TimeDependentCIndex(train.data,validate.data,n.var,B)
alpha<-results[[1]] ## alpha estimation
alpha.pb<-results[[2]] ## alpha perturbation results
alpha
alpha.pb
```



```{r}

head(train.data)
# id is the subject ID; 
# t is the time to recurrent events;
# t.obs is the censoring time;
# indi is the censoring indicator (1-observed; 0-censored);
# Num is the number of recurrent events;
# X1, X2 and X3 are three predictors.  
# 
# Please arrange your data into this format with the same column names.  

```


